The power of dark silicon

### 2018-01-02 toDelete/PositionPaper/lncs-pandoc-master/paper.tex
update files

\hypertarget{conclusion}{%
\subsection{Conclusion}\label{conclusion}}

\begin{itemize}
\tightlist
\item
  oral communication (they think it is more important than written
  texts)
\end{itemize}

\hypertarget{final-words}{%
\section{Final Words}\label{final-words}}

Nec, sodales vitae, vehicula eget, ipsum. Sed nec tortor. Aenean
malesuada. Nunc convallis, massa eu vestibulum commodo, quam mauris
interdum arcu, at pellentesque diam metus ut nulla. Vestibulum eu dolor
sit amet lacus varius fermentum. Morbi dolor enim, pulvinar eget,
lobortis ac, fringilla ac, turpis. Duis ac erat. Etiam consequat.
Integer sed est eu elit pellentesque dapibus. Duis venenatis magna
feugiat nisi. Vestibulum et turpis. Maecenas a enim. Suspendisse
ultricies ornare justo. Fusce sit amet nisi sed arcu condimentum
venenatis. Vivamus dui. Nunc accumsan, quam a fermentum mattis, magna
sapien iaculis pede, at porttitor quam odio at est.

\hypertarget{what-i-ll-focus}{%
\section{What i ll focus}\label{what-i-ll-focus}}

\begin{itemize}
\tightlist
\item
  Explain acceptance unclarity
\item
  Explain Dung's framework
\item
  Explain ASPIC+
\item
  Inconsistencies
\item
  It's higly influenced by the domain knowledge of the analyst
\end{itemize}

@@

\begin{itemize}
\item
  knowledge domain has influence
\item
  analyst domain knowledge is statiscally relevant
\item
  analyst training is even more relevant
\item
  influence of tacit knowlegde in interviews
\item
  ambiguity in interviews - focus on interviewer must have domain
  knowledge
\item
  what i want to do is : possible beneficts in requirement elicitaiton
  is usings two techniques based on the domain knowledge of the analyst,
  sometimes it is good to have an expert and an ignorant of a topic .
\item
  limitations of the technique based on domain knowlegde and tacit
  knowlegde.
\item
  how types of tacit knowlegde may influence in the proposal theory
\item
  how domain knowlegde may influence in the proposal theory
\item
  As an intro:

  \begin{itemize}
  \tightlist
  \item
    analyst domain knowledge is statiscally relevant
  \item
    analyst training is even more relevant
  \end{itemize}
\item
  focus on the technique from the perspective of knowlegde and technique
\item
  future of that technique to solve more complex problems, from the
  prospective of knowlegde and technique
\end{itemize}

@@

>>>>

\hypertarget{effect-of-domain-knowledge-on-elicitation-effectiveness-an-internally-replicated-controlled-experiment}{%
\section{Effect of Domain Knowledge on Elicitation Effectiveness: An
Internally Replicated Controlled
Experiment}\label{effect-of-domain-knowledge-on-elicitation-effectiveness-an-internally-replicated-controlled-experiment}}

The effectiveness of elicitation interviews may be influenced by analyst
skills or characteristics. In these high intensive oral communication
scenario the analyst must be able to draw out relevant information and
needs from the stakeholders. It has been reported that the effectiveness
of the interviews has a direct relation with the domain knowlegde of the
analyst. However, there are also studies suggesting that in somecases
the domain knowlegde have negatives effects in the effectiveness of
interviews.

In this paper {[}2{]}, Aranda et al.~studied the influence of the
analyst domain knowlegde on the effectiveness of elicitation interviews.
The main question they tried to answer was

\emph{Does analyst domain knowledge influence (either positively or
negatively) the effectiveness of the requirements elicitation activity?}

For this purpose, the authors performed the study in two stages. They
performed an initial baseline experiment with two domain problems, and
then they performed an internal replication with two other domain
problems. Furthermore, the authors divided the elicitation process in
two phases. The elication phase which is the actual interview with the
stakeholder, and the reporting phase in which the analyst understands
and documents the information gathered in the elication phase.

One remark of the study is that the authors chose students because of
their lack of experience in eliciation interviews, isolation of the
domain knowledge, and to analyze, in the internal replication, the
influence of the training in requirements engineering in eliciation
interviews. In the study participated post-graduated students as
interviewers and two professors as interviewees. The students should
make open interviews and elicitate the information afterwards. Moreover,
for each domain problem the students were separeted in two groups based
on their level of domain knowlegde, \emph{domain-aware} and
\emph{domain-ignorant}. On the other hand, the effectiveness of the
elicitations was based on the comparison between the number of concepts,
processes and requirements elicitated by the students and the
benchmarks.

The results of the baseline experiment suggest that the domain knowlegde
of the analysts has no significant influence in the effectiveness of the
elicitation interviews. However, the results also suggest that the
domain knowlegde of the interviewees has statistically significant
influence. Supplementary, the results of the internal replication also
suggest that the domain knowlegde of the stakeholders is more relevant
than the analysts', in term of effectiveness of the elicitation
interviews. Nevertheless, these results also show that the possitive
effects of the training in requirements engineering of the interviewers,
with these effects beiang as relevant as interviwees' domain knowlegde.

\hypertarget{what-ill-do}{%
\section{What i'll do}\label{what-ill-do}}

Explain acceptance unclarity Explain Dung's framework Explain ASPIC+
Inconsistencies It's higly influenced by the domain knowledge of the
analyst

@@

knowledge domain has influence analyst domain knowledge is statiscally
relevant analyst training is even more relevant influence of tacit
knowlegde in interviews

ambiguity in interviews - focus on interviewer must have domain
knowledge what i want to do is : possible beneficts in requirement
elicitaiton is usings two techniques based on the domain knowledge of
the analyst, sometimes it is good to have an expert and an ignorant of a
topic .

limitations of the technique based on domain knowlegde and tacit
knowlegde. how types of tacit knowlegde may influence in the proposal
theory how domain knowlegde may influence in the proposal theory

As an intro: analyst domain knowledge is statiscally relevant analyst
training is even more relevant focus on the technique from the
perspective of knowlegde and technique future of that technique to solve
more complex problems, from the prospective of knowlegde and technique

@@

\leavevmode\hypertarget{ref-aranda2016effect}{}%
{[}2{]} A. M. Aranda, O. Dieste, and N. Juristo, ``Effect of domain
knowledge on elicitation effectiveness: An internally replicated
controlled experiment,'' \emph{IEEE Transactions on Software
Engineering}, vol. 42, no. 5, pp. 427--451, 2016.
